FoRTE baseline

### 2019-03-25 analysis/paper/paper.Rmd
[paper] Start working on submodel descriptions

- Radiative transfer
  - Two-stream model (ED default)
    - Same general approach as in CLM 4.5 [@clm45_note], but rather than solving for just two layers (sunlit and shaded), solve for each canopy layer.
    - Set up the two-stream equations for each layer as a linear system and solve the entire set of equations numerically
    - Similar to approaches used in other models: JULES [@mercado_2007_improving], ORCHIDEE-CAN [@naudts_2015_vertically], CLM(SPA) [@bonan_2014_modeling]
  - Multiple scatter model
    - Based on @zhao_2005_multiple
- Crown model
  - Infinite (ED2 default)
    - Marginally taller cohorts completely shade out shorter ones
  - Finite
    - Cohorts have a finite crown area, so multiple cohorts have access to the same light level
    - Based on crown area allometries from @dietze_2008_changing
- Trait plasticity

@@

>>>>

- Radiative transfer
  - Two-stream model (ED default)
    - Same general approach as in CLM 4.5 [@clm45_note], but rather than solving for just two layers (sunlit and shaded), solve for each canopy layer.
    - Set up the two-stream equations for each layer as a linear system and solve the entire set of equations numerically
    - Similar to approaches used in other models: JULES [@mercado_2007_improving], ORCHIDEE-CAN [@naudts_2015_vertically], CLM(SPA) [@bonan_2014_modeling]
  - Multiple scatter model
    - Based on @zhao_2005_multiple
- Crown model
  - Infinite (ED2 default)
    - Marginally taller cohorts completely shade out shorter ones
  - Finite
    - Cohorts have a finite crown area, so multiple cohorts have access to the same light level
    - Based on crown area allometries from @dietze_2008_changing
- Trait plasticity
  - None (ED default) -- Trait values are the same at all canopy heights and light levels
  - Plastic
    - V~cmax~(0) decreases with shading, and SLA increases with shading, based on @lloyd_2010_optimisation

@@

# Appendix 1: Submodel descriptions

## Radiative transfer: Definitions

- $\omega$ -- Clumping factor
- $LAI$ -- Leaf area index
- TAI -- Total area index (leaf and woody area)
- $LAI_e$ / $TAI_e$ -- "Effective" area indices (accounting for clumping)

## Two-stream RTM

<!-- TODO -->

## Multiple scatter RTM

$$ LAI_e = \omega LAI $$

$$ TAI_e = LAI_e + WAI $$

$$ TAI_{l} = \frac{TAI_e}{CAI} $$

Leaf ($w_l$) and wood ($w_w$) weights:

$$ w_l = \frac{LAI_e}{TAI_e} $$
$$ w_w = 1 - w_l $$

Projected area, based on coefficients $\phi_1$ and $\phi_2$.

$$ a_{proj} = \phi_1 + \phi_2 \mu $$

$$ \lambda = \frac{a_{proj}}{\mu} $$
